EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-21 draft.tex
Clarify this @mariosky
Another question for @mariosky
Final comment
Check out this explanation @mariosky

Next, we specify a list indicating which of the 24 benchmark
functions will be tested. In the example, the experiment will use the first five
functions.  The {\em Instances} parameter indicates how many instances of each
function will be tested. {\em Instances}  has a default value of 15. We used this
value because it is the standard for the BBOB benchmark \cite{hansen2016coco}.
In the {\em Dimensions} parameter, we define a list of the dimensions that will
be tested, and we must select additional parameters for each dimension.
According to the maximum number of FEs we mentioned
earlier, we define for each dimension: the number of populations that will be
generated in the setup, and for each population,  the number of generations, and
population size. Finally, the {\em Iterations} parameter indicates how many
complete loops will be performed. % These are generations, right ? - jj
All these parameters give us the maximum
number of FEs that will be performed. For instance, for $D = 2$, the maximum
number of FEs is $200,000$, which is the same as $40*50*10*10$.

@@

When comparing the results in this section, we performed the Wilcoxon Signed-Rank test, with a
significance level of 5\%. We indicate with an asterisk those results that are
not significant.

@@

\begin{table}[h!tbp]
  \caption{Speedup by worker and dimension, taking one worker as the baseline.}
  \label{tab:speedup-table}
  \vspace{0.25cm}
  \centering

@@

\begin{table}[tbp]
  \caption{Median of the number of evaluations required to finish an instance of the function $f_4$ in 30 runs
  with different number of workers and populations}
  \label{tab:evals_instance}
  \vspace{0.25cm}
  \centering

@@

In Table \ref{tab:evals_instance} we can see some additional insights in more
detail. When we increase the number of populations from five to ten, or twenty,
the algorithm needs fewer FEs in both cases. The reduction is more pronounced
when using ten populations, needing fewer FEs in all but a single case (shown in
boldface). In some cases, marked with an asterisk, there is no statistical
difference between the number of evaluations; this happens when using only one
or two workers. The configurations that required less FEs have an underline in
the table.

@@

% Probably a final conclusion should be added here - JJ<

>>>>

Next, we specify a list indicating which of the 24 benchmark
functions will be tested. In the example, the experiment will use the first five
functions.  The {\em Instances} parameter indicates how many instances of each
function will be tested. {\em Instances}  has a default value of 15. We used this
value because it is the standard for the BBOB benchmark \cite{hansen2016coco}.
In the {\em Dimensions} parameter, we define a list of the dimensions that will
be tested, and we must select additional parameters for each dimension.
According to the maximum number of FEs we mentioned
earlier, we define for each dimension: the number of populations that will be
generated in the setup, and for each population,  the number of generations, and
population size. Finally, the {\em Iterations} parameter indicates how many
complete loops, that is, complete message processings, will be performed.
All these parameters give us the maximum
number of FEs that will be performed. For instance, for $D = 2$, the maximum
number of FEs is $200,000$, which is the same as $40*50*10*10$.

@@

When comparing the results in this section, we performed the Wilcoxon Signed-Rank test, with a
significance level of 5\%. We indicate with an asterisk those results that are
not significant. % Where? - JJ

@@

\begin{table}[h!tbp]
  \caption{Speedup by worker and dimension, taking one worker as the
    baseline.}
% Clarify here what you are measuring. Number of evaluations for
% whatever divided by whatever - JJ
  \label{tab:speedup-table}
  \vspace{0.25cm}
  \centering

@@

\begin{table}[tbp]
  \caption{Median of the number of evaluations required to finish an instance of the function $f_4$ in 30 runs
    with different number of workers and populations}
  % But this is total evaluation for all workers, right? - JJ
  \label{tab:evals_instance}
  \vspace{0.25cm}
  \centering

@@

In Table \ref{tab:evals_instance} we try to acquire more insights on
how this works. When we increase the number of populations from five to ten, or twenty,
the algorithm needs fewer FEs in both cases. The reduction is more pronounced
when using ten populations, needing fewer FEs in all but a single case (shown in
boldface). In some cases, marked with an asterisk, there is no statistical
difference between the number of evaluations; this happens when using only one
or two workers. The configurations that required less FEs have an underline in
the table.

@@

% Probably a final conclusion should be added here, including BBOB
% benchmark and the overall performance - JJ
